The paper on \Large \bf Blockchain Frontrunning

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] Submarines done(ish)

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figures/LibSubmarine.png}
\caption{ Submarine implementation~\cite{libsubmarine}. User generates an Unlock transaction from which the commitment address is retrieved. By funding the commitment address, user is commited to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the reveal transaction to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the ``Auction'' is over, anyone can call Finalize function to finilize the process.  \label{fig:LibSubmarine}}
\end{figure}
